Determinism, Complexity, and Predictability in Computer Performance

### 2014-03-26 pecomplexity.tex
added time-series to the title
adding RW Figures

\title{
%Determinism, Complexity, and Predictability in Computer Performance\\
%Quantifying structured complexity and its role in predictability: With applications to predicting computer performance.
%\\ 
Quantifying Predictability through Structural Complexity
%\\ 
%Quantifying Predictability using Structural Complexity 
% \\Decoding Predictability in Complicated Real-Valued Time Series: The balance between complexity and temporal structure
% \\Decoding Complicated Time Series: The balance between complexity and temporal structure and the implications for predictability
}

>>>>

\title{
%Determinism, Complexity, and Predictability in Computer Performance\\
%Quantifying structured complexity and its role in predictability: With applications to predicting computer performance.
%\\ 
{\color{green}Quantifying Predictability through Structural Complexity} 
%\\ 
%Quantifying Predictability using Structural Complexity 
\\Decoding Predictability in Complicated Real-Valued Time Series: The balance between complexity and temporal structure
\\Decoding Complicated Time Series: The balance between complexity and temporal structure and the implications for predictability
}
